% define the various title-page, preamble variables

\newcommand{\firstname}{Kazimierz}
\newcommand{\middlename}{}
\newcommand{\lastname}{Sliwa}
\newcommand{\degrees}{B.Sc.}
\newcommand{\thetitle}{SMA Observations of the Local Galaxy Merger Arp 299}
\newcommand{\halftitle}{SMA Observations of  Arp 299}
\newcommand{\thedegree}{Master of Science}
\newcommand{\shortdegree}{M.Sc.}
\newcommand{\currentmonth}{August}
\newcommand{\currentyear}{2011}
\newcommand{\department}{Physics and Astronomy}
\newcommand{\shortdepartment}{Physics and Astronomy}
\newcommand{\theuniversity}{McMaster University}
\newcommand{\bindingyear}{2011}
\newcommand{\submissionyear}{2011}
\newcommand{\submissionmonth}{August}
\newcommand{\supervisor}{Christine D. Wilson}
\newcommand{\thelocation}{Hamilton, Ontario}
\newcommand{\degreefrom}{University of Toronto}


\newcommand{\firstpages}{\pageref{frontmatterpages}}
\newcommand{\lastpages}{\pageref{finalpage}}


\halftitlepage
\thesistitle
\descriptivenotes

\begin{abstract} 

\input{abstract}

\end{abstract}




\dedication{To my parents}
\begin{acknowledgement}

First, I'd like to thank my supervisor Dr. Christine Wilson. She took a chance on me, who knew nothing of the submillimeter world and I'd like to thank her for giving me the opportunity to work with her.  Her guidance and patience over the last 2 years helped clear and simplify a lot of things. Without her help this project would not have been this awesome. 

I'd also like to thank my committee members Dr. Laura Parker and Dr. Ethan Vishniac for their feedback and comments. I also thank Susanne Aalto for allowing me to use her OVRO CO J=1-0 map of Arp 299 in my research. 

I wish to thank the wonderful friends that I made here at McMaster.  Our coffee runs, softball games and lunch discussions have been fun. A big thanks to my bro and officemate, Max Schirm and my group mate Tara Parkin who I have had many discussions with about research and for helping me along the way. 

Last but not least, I thank my parents who have raised and loved me. This thesis is dedicated to them.
\end{acknowledgement}

\tableofcontents
\listoffigures
%\listofequations%very optional
\listoftables
%\label{lastfirst} 
